The \dealii{} Library, Version 8.4

### 2016-05-03 8.4/deal84.tex
add link to changes

This release of \dealii{} contains a number of large and significant changes
that will be discussed in the following sections. It of course also contains a
vast number of smaller changes and added functionality; the details of these
can be found
\href{https://www.dealii.org/8.4.0/doxygen/deal.II/changes_between_8_3_0_and_8_4.html}{in the file that lists all changes for this release}
and that is linked to from the web site of each release as well as the
release announcement.

@@

The
\href{https://www.dealii.org/8.4.0/doxygen/deal.II/changes_between_8_3_0_and_8_4.html}{file
  that lists all changes for this release} lists another 18
incompatible changes, but none of these should in fact be visible in
typical user codes. Some remove previously deprecated classes and
functions, and the majority change internal interfaces that are not
typically used in user codes.

>>>>

This release of \dealii{} contains a number of large and significant changes
that will be discussed in the following sections. It of course also contains a
vast number of smaller changes and added functionality; the details of these
can be found
\href{https://www.dealii.org/8.4.0/doxygen/deal.II/changes_between_8_3_and_8_4.html}{in the file that lists all changes for this release} (see \cite{changes84})
and that is linked to from the web site of each release as well as the
release announcement.

@@

The
\href{https://www.dealii.org/8.4.0/doxygen/deal.II/changes_between_8_3_and_8_4.html}{file
  that lists all changes for this release} (see \cite{changes84}) lists another 18
incompatible changes, but none of these should in fact be visible in
typical user codes. Some remove previously deprecated classes and
functions, and the majority change internal interfaces that are not
typically used in user codes.
